\documentclass[mim_thesis.tex]{subfiles}
\begin{document}
First of all, a special acknowledgement to my parents, for always supporting me on these crazy choices during my studies of going abroad to experience new cultures and methods of study or work, for showing me the right way to follow and teaching me how to not lose hope and always fight for what I want.

To Samuel Frade, my co-advisor, for all the patience to introduce me to the openEHR world in a detailed way and giving me the idea of this dissertation theme to work in. And for answering my never-ending calls asking for help with Marand tools. And for all the guidance, support and commitment provided on this work. 

To Tina Vavpotič for the constant trust, support, listening, eternal patience and resilience during all the year and not letting me give up when some difficulties appeared. Sometimes living alone in another country can be hard. And also, for the chance to work on Pathfinder.  

To Leandro Gomes, also for the patience and willingness for teaching me how to solve the various bugs that appeared on my script (on a Slovenian keyboard without some special characters, which made this task ten times worse), since programming on web development with new languages and using frameworks like Angular was pretty new for me.

To Aleš Černe and Marko Pipan for the really useful advice and insight about openEHR resources and for teaching me how to deal internally with ADL Designer. To Metod Ribič and Marcel Šalej for, once again, helping me to deal with some issues in the script.

To my advisor, Ricardo Correia for the encouragement and advices given to go abroad on this adventure and learning more about medical informatics in a practical way.

To everyone working at Think!Registry team at Marand, I have learned a lot with all of you.

To Cristina Castro Ribeiro, ECIM course director, for the trust, introduction on the Erasmus programme, advices and concern during all these six years of academic life. 

And at last, but not least, to all the ECIM and Biomedical Engineering praxis group at ISEP for the friendship, for showing me the values of a group that fights for a reason and for giving me the best moments of my academic life. And for always having their “arms wide open” ready for a huge welcoming hug every time I was going back to Portugal.\\

To all of you, a big, big thank you. Without your teaching, encouragement and help, all of this work would not be possible.


\end{document}